---
title: "00_comparing source data"
author: "Sarah Medoff"
date: "December 2, 2022"
output: html_document
code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(tidyverse)
rm(list=ls())

year <- 2022
```

```{r}
source_files.v <- gsub(".RDS", "", list.files(file.path("..", "source")))
```

# Bring in all the source data
```{r}
last_year.l <- lapply(1:length(source_files.v), FUN = function(f){
  readRDS(file.path("..",
                    "..",
                    year-1,
                    "source",
                    paste0(source_files.v[f], ".RDS")))})

#----
this_year.l <- lapply(1:length(source_files.v), FUN = function(f){
  readRDS(file.path("..",
                    "..",
                    year,
                    "source",
                    paste0(source_files.v[f], ".RDS")))})
```

# Find the missing observations 
```{r, warning=FALSE, message=FALSE}
add_obs.l <- lapply(1:length(source_files.v), FUN = function(f){
  
  one_file <- source_files.v[f]
  
  this_year.df <- this_year.l[[f]]
  
  last_year.df <- last_year.l[[f]]
  
  add_obs.one_df <- anti_join(this_year.df, last_year.df)
  
  write.csv(add_obs.one_df, file.path("Additional Observations",
                                  paste0(one_file, ".csv")))
  
  return(add_obs.one_df)
  
})

names(add_obs.l) <- source_files.v
```


# Looking through WP_HAWAII.H_FRS 
```{r}
df <- add_obs.l[[2]]

yr_dist.df <- data.frame(table(substr(df$FISHED_DATE, 1, 4))) %>% 
  rename(Year = Var1,
         Count = Freq) 

ggplot(yr_dist.df, aes(Year, Count)) + 
  geom_point() +
  scale_x_discrete(guide = guide_axis(check.overlap = TRUE))

```
The WP_HAWAII.H_FRS data set in `r year` has `r nrow(df)` different observations than this data set in `r year-1`. 


# Looking through WP_HAWAII.H_INTEGDEALER 
```{r}
df <- add_obs.l[[4]]

yr_dist.df <- data.frame(table(substr(df$REPORT_DATE, 1, 4))) %>% 
  rename(Year = Var1,
         Count = Freq) 

ggplot(yr_dist.df, aes(Year, Count)) + 
  geom_point() +
  scale_x_discrete(guide = guide_axis(check.overlap = TRUE))
```
The WP_HAWAII.H_INTEGDEALER data set in `r year` has `r nrow(df)` different observations than this data set in `r year-1`. 

# Looking through WP_HAWAII_WH.FRS_SPECIES 
```{r}
df <- add_obs.l[[5]]
```
The WP_HAWAII_WH.FRS_SPECIES data set in `r year` has `r nrow(df)` different species than this data set in `r year-1`. 


```{r}
dealer <- read.csv(file.path("Additional Observations", "WP_HAWAII.H_INTEGDEALER.csv"))

dealer_2020 <- dealer %>% 
  filter(REPORT_DATE >= as.Date("2020-01-01") & REPORT_DATE <= as.Date("2021-12-31"))

write_csv(dealer_2020, file.path("Additional Observations", "WP_HAWAII.H_INTEGDEALER_2020.csv"))
```


